PROP

### 2023-08-17 Data & Scripts/BOUT.Rmd
Aug.17 pt.2
Desktop commit

```{r BOUT Dot Plot}
BOUT.DOT<-ggplot(data = BOUT.MEAN
               , aes(x = BEHAVIOR
                     , y = DURATION
                     , color = BEHAVIOR
                     , shape = SENTINEL_PRESENCE))+
  geom_point(position = position_dodge2(width = 0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(DURATION-se)
                    , ymax=(DURATION+se))
                , width = 0.2
                , position = position_dodge(width=0.9))+
  theme_classic() +
  ylab("Mean Bout Duration (s)") +
  scale_colour_manual(values = cbPalette
                      , guide="none") +
  scale_shape_manual(values = c(16,17)
                     , labels = c("Sentinel Absent"
                                  , "Sentinel Present")
                     , name = "") +
  scale_x_discrete(labels = c("Foraging", "Alert", "Moving"))+
  theme(axis.title.x = element_blank()
        , legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin()) +
  facet_grid(~GENERALIZED_ENVIRONMENT)

@@

```{r Disturb}
DF.DOT<-BOUT %>%
    ggplot(aes(x = DISTURBANCE_FREQUENCY
               , y = DURATION
               , color = BEHAVIOR))+
  geom_point(size = 3) +
  theme_classic() +
  labs(x="Mean Bout Duration (s)", y="Disturbances per Minute", color= "Behavior") +
  scale_colour_manual(values = cbPalette, labels = c("Foraging", "Alert", "Moving"))+
  scale_x_continuous(n.breaks=14)
  theme(legend.position = "bottom")

>>>>

```{r BOUT Dot Plot}
BOUT.DOT<-ggplot(data = BOUT.MEAN
               , aes(x = BEHAVIOR
                     , y = DURATION
                     , color = BEHAVIOR
                     , shape = SENTINEL_PRESENCE))+
  geom_point(position = position_dodge(width = 0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(DURATION-se)
                    , ymax=(DURATION+se))
                , width = 0.2
                , position = position_dodge(width=0.9))+
  theme_classic() +
  ylab("Mean Bout Duration (s)") +
  scale_colour_manual(values = cbPalette
                      , guide="none") +
  scale_shape_manual(values = c(16,17)
                     , labels = c("Sentinel Absent"
                                  , "Sentinel Present")
                     , name = "") +
  scale_x_discrete(labels = c("Foraging", "Alert", "Moving"))+
  theme(axis.title.x = element_blank()
        , legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin()) +
  facet_grid(~GENERALIZED_ENVIRONMENT)

@@

```{r Disturb}
DF.DOT<-BOUT %>%
    ggplot(aes(x = DISTURBANCE_FREQUENCY
               , y = DURATION
               , color = BEHAVIOR))+
  geom_point(size = 3) +
  theme_classic() +
  labs(y="Mean Bout Duration (s)", x="Disturbances per Minute", color= "Behavior")+
  scale_colour_manual(values = cbPalette, labels = c("Foraging", "Alert", "Moving"))+
  scale_x_continuous(n.breaks=14)+
  theme(legend.position = "bottom")

### 2023-08-17 Data & Scripts/PROP.Rmd
Aug.17 pt.2
Desktop commit

```{r Open Data}
PROP<-read.csv("DATA.csv", stringsAsFactors = T)

str(PROP)
```
```{r Bout Summary}
source("./Calculate Summary Table with SE, SD, CI by grouping variables.R")
PROP.MEAN <- summarySE(data = PROP
                      , measurevar = "BEHAVIOR_PROPORTION"
                      , groupvars = c("GENERALIZED_ENVIRONMENT"
                                      , "BEHAVIOR"
                                      , "SENTINEL_PRESENCE"
                                      )
                      )
PROP.MEAN
```

@@

```{r Proportion Histograms Individual, include = F}
Untransformed.Prop<-hist(PROP$BEHAVIOR_PROPORTION, breaks=25)
Transformed.Prop<-hist(asin(sqrt(PROP$BEHAVIOR_PROPORTION)), breaks=25)
```

@@

```{r Data Transformation}
PROP$ASIN_PROPORTION<-asin(sqrt(PROP$BEHAVIOR_PROPORTION))
```

@@

```{r PROP Histogram, echo=F}
PROP.HIST<-ggplot(data = PROP) +
  geom_histogram(aes(fill = BEHAVIOR, x = ASIN_PROPORTION)
                 , alpha = 1
                 , bins = 25)+
  scale_fill_manual(values=cbPalette
                    , labels = c("Foraging", "Alert", "Moving"))+
  xlab("Transformed Proportion")+
  ylab("Count")
PROP.HIST
```

@@

```{r PROP MODEL 1}
PROP.MOD1<-lmer(ASIN_PROPORTION~BEHAVIOR+SENTINEL_PRESENCE+GENERALIZED_ENVIRONMENT+BAIT_PRESENCE+GROUP_SIZE+DISTURBANCE_FREQUENCY+(1|VIDEO_ID/ID), data = PROP)

@@

huh, seems like the model is singular. This could mean that the model is overfitted.

@@

```{r PROP MODEL 2}
PROP.MOD2<-lmer(ASIN_PROPORTION~BEHAVIOR*SENTINEL_PRESENCE+BEHAVIOR*GENERALIZED_ENVIRONMENT+SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+GROUP_SIZE+BAIT_PRESENCE+DISTURBANCE_FREQUENCY+(1|VIDEO_ID/ID), data = PROP)

@@

Like MOD1, none of the factors have an effect.

@@

```{r PROP MODEL 3}
PROP.MOD3<-glm(BEHAVIOR_PROPORTION~BEHAVIOR*SENTINEL_PRESENCE+BEHAVIOR*GENERALIZED_ENVIRONMENT+SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+GROUP_SIZE+BAIT_PRESENCE+DISTURBANCE_FREQUENCY, family=quasibinomial, data = PROP)

@@

```{r PROP Post Hoc}
PROP.DIFF<-emmeans(PROP.MOD3, ~BEHAVIOR*SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT, pbkrtest.limit = 5070)
test(pairs(PROP.DIFF, by= "BEHAVIOR"), adjust="fdr")
```

@@

```{r PROP Post Hoc 2}
PROP.DIFF2<-emmeans(PROP.MOD3, ~BEHAVIOR*SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT, pbkrtest.limit = 5070)
PROP.PWISE<-test(pairs(PROP.DIFF2), adjust="fdr")
PROP.PWISE
```

>>>>

```{r Open Data}
DATA<-read.csv("DATA.csv", stringsAsFactors = T)

str(DATA)
```
```{r Bout Summary}
source("./Calculate Summary Table with SE, SD, CI by grouping variables.R")
PROP.MEAN <- summarySE(data = DATA
                      , measurevar = "BEHAVIOR_PROPORTION"
                      , groupvars = c("GENERALIZED_ENVIRONMENT"
                                      , "BEHAVIOR"
                                      , "SENTINEL_PRESENCE"
                                      )
                      )
PROP.MEAN
```

@@

```{r Proportion Histograms Individual, include = F}
Untransformed.Prop<-hist(DATA$BEHAVIOR_PROPORTION, breaks=25)
Transformed.Prop<-hist(asin(sqrt(DATA$BEHAVIOR_PROPORTION)), breaks=25)
```

@@

```{r Data Transformation}
DATA$ASIN_PROPORTION<-asin(sqrt(DATA$BEHAVIOR_PROPORTION))
```

@@

```{r PROP Histogram, echo=F}
PROP.HIST<-ggplot(data = DATA) +
  geom_histogram(aes(fill = BEHAVIOR, x = ASIN_PROPORTION)
                 , alpha = 1
                 , bins = 25)+
  scale_fill_manual(values=cbPalette
                    , labels = c("Foraging", "Alert", "Moving"))+
  xlab("Transformed Proportion")+
  ylab("Count")
PROP.HIST
```

@@

```{r PROP MODEL 1}
PROP.MOD1<-lmer(ASIN_PROPORTION~BEHAVIOR+SENTINEL_PRESENCE+GENERALIZED_ENVIRONMENT+BAIT_PRESENCE+GROUP_SIZE+DISTURBANCE_FREQUENCY+(1|VIDEO_ID/ID), data = DATA)

@@

huh, seems like the model is singular. This could mean that the model is over fitted.

@@

```{r PROP MODEL 2}
PROP.MOD2<-lmer(ASIN_PROPORTION~BEHAVIOR*SENTINEL_PRESENCE+BEHAVIOR*GENERALIZED_ENVIRONMENT+SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+GROUP_SIZE+BAIT_PRESENCE+DISTURBANCE_FREQUENCY+(1|VIDEO_ID/ID), data = DATA)

@@

Like MOD1, none of the factors have an effect. Still singular.

@@

```{r PROP MODEL 3}
PROP.MOD3<-glm(BEHAVIOR_PROPORTION~BEHAVIOR*SENTINEL_PRESENCE+BEHAVIOR*GENERALIZED_ENVIRONMENT+SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+GROUP_SIZE+BAIT_PRESENCE+DISTURBANCE_FREQUENCY, family=quasibinomial, data = DATA)

@@

```{r PROP Post Hoc}
PROP.DIFF<-emmeans(PROP.MOD3, ~BEHAVIOR*SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT)
test(pairs(PROP.DIFF, by= "BEHAVIOR"), adjust="fdr")
```

@@

```{r PROP Post Hoc 2}
PROP.DIFF2<-emmeans(PROP.MOD3, ~BEHAVIOR*SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT)
PROP.PWISE<-test(pairs(PROP.DIFF2), adjust="fdr")
PROP.PWISE
```
